Figuras presentacion Lab, Nov 2020

### 2020-11-19 Figuras presentacion lab.Rmd
Fig comp x sp

```{r Pelecanus}

@@

OcuI_Pel+OcuP_Pel
```

```{r Larus}
Species_DFInv_Larus <- Species_DFInv %>% dplyr::filter(Species=="Larus")
Species_DFPrim_Larus <- Species_DFPrim %>% dplyr::filter(Species=="Larus")

@@

OcuI_Larus + OcuP_Larus
```

```{r Larosterna}
Species_DFInv_Larosterna <- Species_DFInv %>% dplyr::filter(Species=="Larosterna")
Species_DFPrim_Larosterna <- Species_DFPrim %>% dplyr::filter(Species=="Larosterna")

@@

OcuI_Larosterna + OcuP_Larosterna
```

```{r Columba}
Species_DFInv_Columba <- Species_DFInv %>% dplyr::filter(Species=="Columba")
Species_DFPrim_Columba <- Species_DFPrim %>% dplyr::filter(Species=="Columba")

@@

OcuI_Columba + OcuP_Columba
```

@@

```{r Comportamineto, fig.height=8, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

@@

P <-ggplot(ComportamientoPrim) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

layout <- "
AAAAAAAA
BBBBBBB#
"
I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')

@@

```{r CompLarus, fig.height=8, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

P <-ggplot(ComportamientoPrim) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

layout <- "
AAAAAAAA
BBBBBBB#
"
I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')

>>>>

```{r Pelecanus, fig.width=12}

@@

OcuI_Pel/ OcuP_Pel
```

```{r Larus, fig.width=12}
Species_DFInv_Larus <- Species_DFInv %>% dplyr::filter(Species=="Larus")
Species_DFPrim_Larus <- Species_DFPrim %>% dplyr::filter(Species=="Larus")

@@

OcuI_Larus / OcuP_Larus
```

```{r Larosterna, fig.width=12}
Species_DFInv_Larosterna <- Species_DFInv %>% dplyr::filter(Species=="Larosterna")
Species_DFPrim_Larosterna <- Species_DFPrim %>% dplyr::filter(Species=="Larosterna")

@@

OcuI_Larosterna / OcuP_Larosterna
```

```{r Columba, fig.width=12}
Species_DFInv_Columba <- Species_DFInv %>% dplyr::filter(Species=="Columba")
Species_DFPrim_Columba <- Species_DFPrim %>% dplyr::filter(Species=="Columba")

@@

OcuI_Columba / OcuP_Columba
```

@@

```{r Comportamineto, fig.height=8, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")

@@

P <-ggplot(ComportamientoPrim) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+ ggtitle("Primavera")

layout <- "
AAAAAAAA
BBBBBBB#
"
I + P + plot_layout(design = layout)

@@

```{r CompLarus, fig.height=7, fig.width=7}
ComportamientoInv_Larus <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")

I <-ggplot(ComportamientoInv_Larus) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")

ComportamientoPrim_Larus <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")

P <-ggplot(ComportamientoPrim_Larus) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
  ggtitle("Primavera")

I / P 
```

```{r CompPele, fig.height=7, fig.width=7}
ComportamientoInv_Pele <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")

I <-ggplot(ComportamientoInv_Pele) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")

ComportamientoPrim_Pele <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")

P <-ggplot(ComportamientoPrim_Pele) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
  ggtitle("Primavera")

I / P 
```

```{r CompLarosterna, fig.height=7, fig.width=7}
ComportamientoInv_Larosterna <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")

I <-ggplot(ComportamientoInv_Larosterna) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")

ComportamientoPrim_Larosterna <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")

P <-ggplot(ComportamientoPrim_Larosterna) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
  ggtitle("Primavera")

I / P 
```

```{r CompColumba, fig.height=7, fig.width=7}
ComportamientoInv_Columba <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Columba_livia")

I <-ggplot(ComportamientoInv_Columba) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")

ComportamientoPrim_Columba <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Columba_livia")

P <-ggplot(ComportamientoPrim_Columba) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
  ggtitle("Primavera")

I / P 
```
